Plant-pollintor networks worldwide are composed by the same specific building

### 2021-10-12 Draft/Draft.Rmd
fixing mistake

The observed functional group probabilities on the different positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**) suggesting the existance of ecological processes shaping their structure. In addition, we found that just 30% of the observed motif combinations took place. This restricted set of possible combinations is no surprise, because sampling the full set of interactions is tremendously complex and a large portion of the possible interactions do not take place because of life history constraints [@jordano2016]. Thus, similarly to the presence of forbidden links, we found the existence of forbidden motifs.

---
THIS IS A COMMENT
3) Ecology is complex, combinations not recovered by positions. This is a very cool result, because imply that knowing the probabilities of each position is not enough to predict network realizations.
---

@@

---
THIS IS ACOMMENT
4) Limitations (but keep it short and simple): FG are hard to describe, bias in sampling worldwide, …

@@

- Paper of Poisot 2020
---

---
THIS IS A COMMENT
5) Future direction and conclusions (also short). This opens the door to help predicting novel interactions beyond pairwise interactions. We not only know now how the building blocks are structures, but also that who conform this building blocks is not random.
---

>>>>

The observed functional group probabilities on the different positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**) suggesting the existance of ecological processes shaping their structure. In addition, we found that just 30% of the observed motif combinations took place. This restricted set of possible combinations is no surprise, because sampling the full set of interactions is tremendously complex and a large portion of the possible interactions do not take place because of life history constraints [@jordano2016]. Thus, similarly to the presence of these forbidden interactions, we found also the existence of forbidden motifs.

---
Thus, similarly to forbidden links, we found the existence of forbidden motifs. Hence, trait-matching

Trait matching example and a ref...
Phenology example with a ref...
Co-occurence...

3) Ecology is complex, combinations not recovered by positions. This is a very cool result, because imply that knowing the probabilities of each position is not enough to predict network realizations.

@@

4) Limitations (but keep it short and simple): FG are hard to describe, bias in sampling worldwide, …

@@

- Paper of Poisot 2020

5) Future direction and conclusions (also short). This opens the door to help predicting novel interactions beyond pairwise interactions. We not only know now how the building blocks are structures, but also that who conform this building blocks is not random.
---
